Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-11 Tex/elsevier/reply Solar Energy JULY 2019.tex
solar energy revised text

@@

@@

>>>>

\begin{resposta} 
We thank the kind comment provided by this reviewer. Indeed, it summarizes what was intended to be done with this manuscript. In addition, we should highlight that the main focus was at the validation process of the PV system, instead of the mathematical modelling that was investigated in prior studies over the last two decades. This information was carefully included at the revised Abstract, Introduction and at the Conclusion sections.

Regarding the Figure 2, we did as highlighted by the reviewer. Moreover, we did the same to voltage V in order to keep the same standard.

@@

\begin{resposta} 
Indeed, we miss this information at paragraph that describes the Figure. We thank you so much for this observation. Therefore we revised the text and described every symbol. The final version of the paragraphs were: "A stand-alone PV system is illustrated in Fig.1. The PV generator is a semiconductor device that can convert solar energy into DC electricity, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$. For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter). The AC load dictates the behavior of AC electrical load from the house that will be fed by the system. At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.".
\end{resposta}

@@

\begin{resposta} 
Indeed, we did not inform the impact the changing of computer setup or related issues. We thank you so much for this observation. Therefore we revised the text and included the following paragraph: "Note that the results presented here depend on the computer's processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved. Additionally, any change from HOMER Pro to another simulation tool can influence the measured time to obtain results.".
\end{resposta}

### 2019-07-11 Tex/elsevier/trindade_solar_energy_rev1.tex
solar energy revised text

\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to validate any kind of system. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. Case studies, from real photovoltaic systems deployed in five different sites, ranging from 700 W to 1,200 W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated as well, in order to compare performance and soundness. Data from practical applications show the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.
\end{abstract}

@@

@@

A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}. The PV generator is a semiconductor device that can convert solar energy into DC electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter). The AC load dictates the behavior of AC electrical load from the house that will be fed by the system.

@@

\textcolor{red}{Note that the results presented here depend on the computer’s processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved. Additionally, any change from HOMER Pro to another tool can influence the measured time of the algorithms.}

@@

We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.

>>>>

\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In 2017, for the first time, the number of people without access to electricity dipped below 1 billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design space. Automated verification using model checking has proven to be an effective technique to validate \textcolor{red}{complex systems}. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system including solar panel, charge controller, battery, inverter, and electric load. \textcolor{red}{Therefore the focus is in the solar photovoltaic project validation, as intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior. Case studies, ranging from 700 W to 1,200 W}, were used to evaluate this proposed approach and to compare that with specialized simulation tool. Different verification tools were evaluated as well, in order to compare performance and soundness among automated tools. \textcolor{red}{The results reported by the automated verification and by the simulation tools were compared with data collected from dwellers of the deployed cases, showing the effectiveness of our approach, where specific conditions that lead to failures in a photovoltaic solar system are only detailed by the automated verification method.}
\end{abstract}

@@

\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems. Instead, our novelty relies on an effective approach to perform validation of PV systems using formal methods, in a process that is intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.}

@@

A stand-alone PV system is illustrated in Fig.\ref{fig:blockdiagram}. The PV generator is a semiconductor device that can convert solar energy into DC electricity\textcolor{red}{, with high dependence of two weather variables from the site where the system is deployed: solar irradiance $G$ and temperature $T$}. 
For night hours or rainy days, power stored in batteries can be used and it implies the presence of a charge controller~\citep{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required (inverter). The AC load dictates the behavior of AC electrical load from the house that will be fed by the system. \textcolor{red}{At this pictured modular structure, every element produces/consumes current $I$ and voltage $V$ as illustrated by their physical magnitudes, where $pv$ means photovoltaic, $bat$ is battery, $dc$ is direct and $ac$ is alternating signals.}

@@

\textcolor{red}{Note that the results presented here depend on the computer's processor and memory, the version of each tool (CBMC, ESBMC, CPAchecker), the parameters passed by the command-line, and the algorithm to be solved. Additionally, any change from HOMER Pro to another simulation tool can influence the measured time to obtain results.}

@@

We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. 
\textcolor{red}{The focus was on the method to validate PV systems projects, based on formal methods that can cover the design-space better than simulation tools. 
We have considered five case studies, ranging from $700$ W to $1,200$ W; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro). The results from automated verification and simulation tools were confronted with information collected from dwelles of the sites where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
